Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2017-04-25 Draft_2.tex
Proof Reading Completed

    \end{center}
\end{titlepage}
\
\vfill
\begin{center}This 
	\textbf{Abstract}
\end{center} 
\label{sec:Abstract}
Semantic Analysis is the process of giving meaning to the tokens of a sentence. This process has a multitude of applications from speech recognition to unsepervised knowledge aquisition. Current solutions do not provide enough accuracy to be relied upon fully for these puposes, making it a heated area of research. It is known that humans are very good at semantic analysis, and multiple psychologial models describing this exist, such as the Working Memory Model. The focus of this report is a computational model, derived from these theories, with the intention of providing a more reliable solution to the problem of semantic analysis. A subset of the working memory model is used, in conjunction with hyponymy base activation and disambiguation. The model developed provides an acccuracy greater than some approaches, though, without further development, fails to reliably identify word meanings across a large input corpus. The results implicate the need for the use of a greater number of semantic links in order to correctly derive meaning.

@@

Natural language is the language spoken and written by humans. It is very powerful, though its key downfall is its ambiguity. The study of natural language processing aims to allow a computer to understand natural language, and formulate a relevant response based upon its input. Within this, the problem of input text analysis has traditionally been broken down into smaller sub-problems \cite{NLPHandbook}:

\begin{itemize}
	\item \textbf{Text Preprocessing} \\
	Before any analysis can take place, the input raw text must be converted into a usable format \cite{NLPHandbook}.
	\item \textbf{Lexical Analysis} \\
	One word can have multiple forms, for example ”judge” (the lemma) has the forms {”judge”, ”judges”, ”judging”, ”judged”} (morphological variants). The job of Lexical Analysis is to replace all morphological variants of a word, with their corresponding lemma, a process known as stemming \cite{NLPHandbook}.
	\item \textbf{Syntactic Parsing} \\
	When deriving meaning from sentences, the grammatical structure can provide important insight. The Syntactic parsing technique extracts this information using Part-of-Speech tagging (detecting syntactic role) and Chunking (detecting noun and verb phrases) \cite{NLPHandbook}.
	\item \textbf{Semantic Analysis} \\
	The derivation of meaning from the sentences tokens \cite{NLPHandbook}. 
\end{itemize}

@@

	\item \textbf{The Summarisation of Documents} is a problem that has been partially solved by \hyperref[sec:TFIDF]{TF-IDF}. The summarisation could be improved by the aquisition of information regading text meaning.

@@

It can be seen that the study of the brain's processes of semantic analysis, and their application to a computational model, could provide a satisfying solution. A great deal of research is directed at studying these processes, largely influenced by the working memory model proposed by Baddeley \cite{MemoryBaddeleyEysenkAnderson}. This memory model describes a system of structures, which work in conjunction with one another to form a representation of the brain’s input.

@@

In the introduction, the basic motivations behind this project were laid out. This literature review aims to describe, and discuss, the previous research, upon which this project is built. The following section will cover Psycholinguistics, previous work on semantic analysis, as well as some of the tools that are used throughout the implementation.

%------------ Memory Models
\subsection{Psycholinguistics}
\label{sec:Psycholinguistics}
The understanding of Natural language is a problem with which the human brain performs extremely well. From this satatement, it can be derived that a computational solution could be effectively built around knowledge of the processes at work in the brain. The process of language comprehension can be described, in part, using the working memory model\cite{MemoryBaddeleyEysenkAnderson}.

According to Baddely et al. \cite{MemoryBaddeleyEysenkAnderson} there exist multiple, special purpose, memory structures within two main categories, the Short-term Memory and the Long-term Memory. The working memory model describes how information can pass between the different structures, either originating from the Long-term Memory, or sensory inputs \cite{MemoryBaddeleyEysenkAnderson}.

\subsubsection{Long-term Memory}
\label{LongTerm}
The long-term memory (LTM) contains semi-permanent information. Within the LTM, there exist Explicit and Implicit memory structures. The contents of the Implicit memory describe skills and methods of doing things, whereas the Explicit memory contains factual information\cite{MemoryBaddeleyEysenkAnderson}. When considering these structures, it can be seen that Explicit memory is of greater interest in the context of NLP.

@@

\subsubsection{Short-term Memory}
\label{ShortTerm}
The short-term memory (STM) is a structure of limited capacity, used to store items for periods usually of no more than a few seconds \cite{MemoryBaddeleyEysenkAnderson}. In 1955, G. Miller, based upon previous experimental results, concluded that the size of the STM existed in the realm of 7$\pm$2 items of information \cite{SevenPlusMinusTwo}.

@@

\subsubsection{Episodic Buffer}
\label{sec:EpisodicBuffer}
When considering the reading of text, it was found that participants were able to recall significantly more than 7$\pm$2 items of information. In 2000, a structure linking the STM and LTM was proposed by Baddely \cite{BaddeleyEpisodicBuffer}. The Episodic Buffer makes use of sensory data to store information too old to exist in the STM, without committing it to the LTM. This often occurs through the use of imagery to represent a set of concepts \cite{MemoryBaddeleyEysenkAnderson}. When applied to natural language, this memory structure allows the representation of a greated context than the STM alone.

\subsubsection{Disambiguation Models}
\label{sec:DisambiguationModels}
In some cases, when assigning meaning to words, ambiguity can arise. Some words have multiple concepts, for example, bank can refer to a building, or a sloped surface alongside a body of water. In such cases, the brain uses some process to select the correct concept. One such model of this disambiguation is the Multiple-access model \cite{PsychologyOfLanguage}.

According to the multiple-access model, when presented with an ambiguious word, initially all corresponding concepts are activated \cite{AccessingLexicalAmbiguities}. The most appropriate concept is then chosen using a balance of context and frequency.

@@

%------------ WORDNET
\subsection{Wordnet}
\label{Wordnet}
In order to build a successful system, within the time bounds given by this project, a good, preexisting, model of semantic memory is required. One such example of this is Wordnet \cite{WN1Introduction}.

@@

\label{Synsets}Central to the design of Wordnet, is the idea of synsets \cite{WN1Introduction}. The authors began using the assumption that all word meanings can be uniquely defined by their set of synonyms (words which share like meaning). In most cases, this assumption holds true, though, in cases where more detail is required, a "gloss" was added \cite{WN1Introduction}.

@@

It is common knowledge that words can fall into one of a number of categories, nouns, adjectives, verbs and adverbs. G. Miller et al. note that, due to the differences in the relations between words in these categories, each type has differs in the structure they imply, and are therefore held in different files \cite{WN1Introduction}. The proceeding subsections will go into each of these categories in more detail.

\subsubsection{Nouns}
\label{Nouns}
G. Miller et al. note that a noun can be defined using only its immediate hypernym, and how it differs from the other hyponyms of its immediate hypernymh \cite{WN2Nouns}. From this, it can be seen that hyponymy is perhaps the most important relation in the organisation of nouns. For this reason, nouns form a strong hierachical structure in Wordnet.

Wordnet's designers stated the assumption that all nouns can be contained in a single hierachial structure \cite{WN2Nouns}. The issue with having a single word, of which all other words are hyponyms, is that this hypernym is relatively meaningless. It was instead decide to divide all words into 25 separate files, each containing a hierachical tree beginning with one of the following synsets \cite{WN2Nouns}:

@@

\subsubsection{Adjectives}
\label{Adjectives}
Adjectives in can be divided into four distinct groups, each implying a different structure of semantic links \cite{WN3Adjectives}:
\begin{itemize}
	\item Descriptive Adjectives
	\begin{itemize}
		\item As stated in the \hyperref[Nouns]{previous section}, nouns have attributes. Descriptive adjectives act as modifiers for these attributes: for example, a building has a height, by saying "tall building", the height attribute is given a value \cite{WN3Adjectives}. Antonymy, defined \hyperref[Antonym]{previously}, is considered by wordnet's designers to be the most important relation between descriptive adjectives. Unfortuantely, not all adjectives have antonyms, leading to the designer's addition of an indirect antonym" semantic link, between synonyms of a word and its antonym \cite{WN3Adjectives}. These semantic links give rise to a structure made up of pairs, linked to one another by their synonyms.
	\end{itemize}

@@

	\item Colour Adjectives
	\begin{itemize}
		\item As their name suggests, colour adjctives concern the value of the colour attribute. This definition implies that these words should, in fact, fit into the descriptive adjective category. Their separation is given by colour adjectives lack of true antonym (excluding modifiers such as "light" and "dark") \cite{WN3Adjectives}. The lack of clear semantic relations between these words poses a problem for their organisation, leading wordnet's designers to link them using their definitions, i.e. using hue, lightness and saturation.
	\end{itemize}

@@

\textbf{Entailment} is a relation, simlar in nature to hyponymy. A verb (a) is said to entail another (b) if, when b is substituted for a in a sentace, the truth value of the sentance remains the same \cite{WN4Verbs}. For example, "run" entails "move", "she ran" can also be described by "she moved". If a entails b, and b entials a, a and b are synonyms.

@@

\subsubsection{Latent Semantic Analysis}
\label{sec:LSA}
In 1997, T. Laundaur and S. Dumais proposed a purely statistical method of semantic analysis, called Latent Semantic Analysis (LSA) \cite{LatentSemanticAnalysis}. The model can be visualised as a set of nodes, each representing a word, existing in semntic space. Words placed close together can be said to have similar meaning, and when close enough together, can be called synonyms.

@@

The authors found that, when presented with a synonym test, the model's best performance gave 64.4\% correct answers , which, when compared to US undergraduates for whom English is not their first language (scoring 64.5\% on average), could be considered to be reasonably effective \cite{LatentSemanticAnalysis}. This model only considers likelyhood, which, as discussed in the \hyperref[sec:DisambiguationModels]{Disambiguation Models section}, is only one of the two methods the brain is theorised to use for this process. By using a similar method in conjunction with a context focused model, a more accurate and useful model could be produced.

@@

As words in a document were encountered, all of its synsets were activated. All hypernyms, to a specified depth were also activated. The output of the system was the set of the most commonly seen synsets across the entire document, according toan equation similar to that discussed earlier in this subsection \cite{SeddingKazakov}.

@@

\subsubsection{Neural Networks}
\label{sec:NeuralNetwork}
In recent years the use of Neural Networks, more specifically deep learning Neural Networks, in the solving of computational problems has dramatically increased. More recently, this technique has been applied to the problem of natural language processing. From the description of Natural Language Processing given in the \hyperref[sec:IntroContext]{introduction}, we can see that a large proportion of NLP is the assigning of labels to tokens within a sentence. This process of labelling may also be interpreted as a categorisation problem, which Neural Networks are wellsuited to, and are often associated with \cite{NeuralNetworks}.

The first process requrired in the use of neural networks, is the conversion of raw text into a numerix, vector-based representation, capable of being processed. The sentence is then passed into the neural network \cite{NeuralNetworks}. The network proposed by R.Collobert and J. Weston in 2008 contained multiple layers, each serving its own purpose \cite{NeuralNetworks}. Initially the network identifies word features, before using this data to calculate the probability of each synset of each word.

@@

Unfortunately, the model failed to produce the correct synset significantly more accurately than the author's baseline (selecting the most common synset) \cite{MattBurkePrevious}. As suggested in the report, this may be due to semantic links, which occur in the brain, not being available or utilsed by the model. Though, it may also be the case that the mathematical models used were inaccurate, with less linear functions being required.

The memory structures use may also have contributed to the result. Each item in the LTM had an activation \cite{MattBurkePrevious}. This activation is not present in the models developed by Baddeley, Shiffrin and Atkinson \cite{MemoryBaddeleyEysenkAnderson, ControlProcessesSTMAtkinson}.

@@

An implementation of an STM should have a finite size, falling in the range defined by G. Miller, 7$\pm$2.  Atkinson and Shiffrin’s model requires that the implemented STM contains items originating from a combination of the systems input, and LTM, each with an activation. The structure’s contents must also change, according the arrival of new items, so as to correctly represent the local context of a section of text.

The systems LTM (Semantic Memory) requires knowledge of a large number of word meanings. Each of the meanings should be coupled with useful information consisting of a number of semantic links, connecting them to other meanings. As discussed in section \ref{Wordnet}, WordNet is a capable, pre-existing database, which follows a similar structure to the LTM defined by Baddeley. For this reason, it should be used to ensure that as much semantic information can be contained in the LTS as possible within the time scale of the project.

The addition of an Episodic Buffer may also be beneficial. Baddeley’s proposal may prove difficult to implement fully within the scope of this project, so design decisions must be made to simplify the model. With that said, its functionality must remain reasonably consistent, the representation of wider context, for it to prove useful to the system.

@@

In the multiple access model, all relevant concepts are activated when a word is encountered.  A successful reading system should change the contents of the STM using a series of activations. If a concept already exists in the STM, Atkinson and Shiffrin’s model’s process of rehearsal should be employed, increasing the concepts actviation.

@@

Before a document can be inputted, it must have been syntactically analysed. Each word in a correctly preprocessed document will have a PoS tag, signifying its purpose in the sentance. This tag can then be used to minimise the size of the set of each word's possible definitions.

@@

Upon activation, the synset in question's activation is increased by an amount, dependant upon the hypernym model used (discussed later in this section). The same synset can be activated multiple times within the same sentence, an example of which is shown in Figure \ref{fig:HypernymAct}. In this case, a similar model to \hyperref[sec:MattBurke]{that proposed by M. Burke} \cite{MattBurkePrevious} is used: 
\[H = \sum\limits_{i=1}^N S_i\] 
The total acivation increase of a synset is equal to the sum of all its activations within the sentence.

@@

\begin{itemize}
	\item The activation increase of the words hypernyms must decrease as their generality increases, i.e.  as they become closer to the top of the tree.

@@

\subsubsection{Episodic Buffer}
\label{sec:ImplementedEpisodicBuffer}
The Episodic Buffer described in section \ref{sec:EpisodicBuffer} makes use of imagery generated by sensory data to store information \cite{BaddeleyEpisodicBuffer}. A memory structure modelling this process exactly would not be possible within the scope of this project, therefore, a simplified model had to be created. In this simplified model, the Episodic Buffer still provides a memory for wider context, but does so using a synsets, not imagery.

@@

The most notable use of the Memory Controller is the activation of synsets. In order to activate a synset, the Memory Controller must take into account the whether the synset is present in any of the afformentioned memory structures, and handle the activation accordingly. The activateSynset function, shown in Listing \ref{lst:activateSynset} is responsible for handling this process.

@@

\subsubsection{Context}
\label{sec:DisambiguationContext}
The first approach attempted by the system makes use of the local context of a word. This context is held the STM, and used in conjunction with knowledge of noun-verb relationships (the latter is discussed in Section \ref{sec:Sanity}). Two algorithms for disambiguation using this approach have been implemented, one using hyponyms and one using hypernyms.

@@

It may be noted that sanityCheck only considers verb incorrectness. As stated in the \hyperref[Verbs]{WordNet section}, for each word, there is likely to be a larger set of synsets when compared to nouns. With this knowledge, we can assume that the likelyhood of an incorrect result for a verb is higher than that of a noun.

@@

For the purposes of parameter adjustment, the system will be tested on a single document. By limiting the input size, the time taken for each test can be reduced. Though appropriate for parameter tuning, it can be seen that a limited input size will not provide a good indication of general performance. For this reason, after parameter tuning has occured, the optimal values will be used in a more thourough evaluation test. This test will provide an input of 5 documents, ranging accross a variety of topics.

@@

The aim of the STM is to represent the local context of a word during the disambiguation phase. This requires of degree of generality in the contents of the STM, in order to  provide a wider view of a set of sentences contents. A high number of synsets directly seen would imply that the either, the local context of a word is not strong, or the contents of the STM are less general than intended. The latter can be seen as a failure to correctly represent the local context. An effective STM would contain hypernyms of the words in each sentence, meaning the more general concepts of the context are represented.

@@

When tested, this system performs significantly better than \hyperref[sec:EvFrequency]{random chance}, with an accuracy of 12\%. Even though it is an improvement, it can be seen that Frequency alone does not produce a satisfying result. From this, we can tell that frequenncy only plays a small part in the disambiguation of text, and contextual information is required for a more effective system.

@@

Given the results of this test, it has een decided that 5 is the optimal size for the STM. When presented with a larger number of test documents, the system performs with an accuracy of 35\%, having 45\% of synsets directly seen in the STM. This is significantly better performance than \hyperref[sec:EvFrequency]{ a system based solely on frequency}.

@@

Given the results shown in table \ref{table:bActivation}, it can be seen that a value of 1 for $b$, achieves the best balance between accuracy and the number of synsets directly seen. With more testing data, the system produces an accuracy of 35\%. This is no imporvement from the previously used method. Though the accuracy has remained consistent, only 39\% of synsets were directly seen, implying more generality in the STM, without loss of performance.

\subsection{Episodic Buffer}
\label{sec:EvEpisodicBuffer}
The episodic buffer, described in section \ref{sec:ImplementedEpisodicBuffer} aims to provide a more global context than the STM. With the functionality of the buffer being relatively simple, only one varibale exists, the boost provided by a previously seen synset, with a greater boost giving global context a larger impact on disambiguation. The size of this boost will be varied between 0 (i.e. no episodic buffer) and 2.

@@

When observing the performance of the noun STM, it can be seen that there exists some abiguity, with some words having multiple possible meanings in the STM. In these cases, it can be seen that there exist few possible options for each word. From this we can say that the system has minimised the number of possibilities for each option.

When compared to the noun STM, the verb STM contains much more abiguity. This is likely due, in part, to the larger number of possible meanings for each word. This effect was not unexpected,hence the inclusion of sanity checks, described in section \ref{sec:Sanity} Though these were shown to be ineffective in an earlier section.

@@

\section{Conclusions}
\label{sec:Conclusions}
This project has aimed to utlise previously established psychological models of disambiguation, and apply them to the problem of Semantic Analysis. The models used are those originally developed by Atkinson and Shiffrin \cite{ControlProcessesSTMAtkinson}, and then later further studied by Baddeley, to ultimately produce the Working Memory Model \cite{MemoryBaddeleyEysenkAnderson}.

@@

	\item \textbf{Reading System} \newline
		The system uses atctivation and forgetting to model the same prrocesses which exist in Atkinson and Shiffrin's model \cite{ControlProcessesSTMAtkinson}. As the input corpus is read, these processes occur for each word, causing context to be represented by the STM and Episodic Buffer.

>>>>

    \end{center}
\end{titlepage}
\
\vfill
\begin{center} 
	\textbf{Abstract}
\end{center} 
\label{sec:Abstract}
Semantic Analysis is the process of giving meaning to the tokens of a sentence. This process has a multitude of applications from speech recognition to unsepervised knowledge aquisition. Current solutions do not provide enough accuracy to be relied upon fully for these puposes, making it a heated area of research. It is known that humans are very good at semantic analysis, and multiple psychologial models describing this exist, such as the Working Memory Model. The focus of this report is a computational model, derived from these theories, with the intention of providing a more reliable solution to the problem of semantic analysis. A subset of the working memory model is used, in conjunction with hyponymy based activation and disambiguation. The model developed provides an acccuracy greater than some approaches, though, without further development, fails to reliably identify word meanings across a large input corpus. The results implicate the need for the use of a greater number of semantic links in order to correctly derive meaning.

@@

Natural language is the language spoken and written by humans. It is very powerful, though its key downfall is its ambiguity. The study of natural language processing (NLP) aims to allow a computer to understand natural language, and formulate a relevant response based upon its input. Within this, the problem of input text analysis has traditionally been broken down into smaller sub-problems \cite{NLPHandbook}:

\begin{itemize}
	\item \textbf{Text Preprocessing} \\
	Before any analysis can take place, the input raw text must be converted into a usable format \cite{NLPHandbook}.
	\item \textbf{Lexical Analysis} \\
	One word can have multiple forms, for example ”judge” (the lemma) has the forms {”judge”, ”judges”, ”judging”, ”judged”} (morphological variants). The job of Lexical Analysis is to replace all morphological variants of a word, with their corresponding lemma, a process known as stemming \cite{NLPHandbook}.
	\item \textbf{Syntactic Parsing} \\
	When deriving meaning from sentences, the grammatical structure can provide important insight. The Syntactic parsing technique extracts this information using Part-of-Speech (PoS) tagging (detecting syntactic role) and Chunking (detecting noun and verb phrases) \cite{NLPHandbook}.
	\item \textbf{Semantic Analysis} \\
	The derivation of meaning from the sentences tokens \cite{NLPHandbook}. 
\end{itemize}

@@

	\item \textbf{The Summarisation of Documents} is a problem that has been partially solved by \hyperref[sec:TFIDF]{TF-IDF}. The summarisation could be improved by the aquisition of information regarding text meaning.

@@

It can be seen that the study of the brain's processes of semantic analysis, and their application to a computational model, could provide a satisfying solution. A great deal of research is directed at studying these processes, largely influenced by the Working Memory model proposed by Baddeley \cite{MemoryBaddeleyEysenkAnderson}. This memory model describes a system of structures, which work in conjunction with one another to form a representation of the brain’s input.

@@

In the introduction, the basic motivations behind this project have been established. This literature review aims to describe, and discuss, the previous research, upon which this project is built. The following section will cover Psycholinguistics, previous work on semantic analysis, as well as some of the tools that are used throughout the implementation.

%------------ Memory Models
\subsection{Psycholinguistics}
\label{sec:Psycholinguistics}
The understanding of natural language is a problem with which the human brain performs extremely well. From this statement, it can be derived that a computational solution could be effectively built around knowledge of the processes at work in the brain. The process of language comprehension can be described, in part, using the Working Memory model\cite{MemoryBaddeleyEysenkAnderson}.

According to Baddely et al. \cite{MemoryBaddeleyEysenkAnderson} there exist multiple, special purpose, memory structures within two main categories, the Short-term Memory and the Long-term Memory. The Working Memory model describes how information can pass between the different structures, either originating from the Long-term Memory, or sensory inputs \cite{MemoryBaddeleyEysenkAnderson}.

\subsubsection{Long-term Memory}
\label{LongTerm}
The long-term memory (LTM) contains semi-permanent information. Within the LTM, there exist explicit and implicit memory structures. The contents of the Implicit memory describe skills and methods of doing things, whereas the Explicit memory contains factual information\cite{MemoryBaddeleyEysenkAnderson}. When considering these structures, it can be seen that Explicit memory is of greater interest in the context of NLP.

@@

\subsubsection{Short-term Memory}
\label{ShortTerm}
The short-term memory (STM) is a structure of finite capacity, used to store items for periods usually of no more than 15-30 seconds \cite{MemoryBaddeleyEysenkAnderson}. In 1955, G. Miller, based upon previous experimental results, concluded that the finite size of the STM existed in the realm of 7$\pm$2 items of information \cite{SevenPlusMinusTwo}.

@@

\subsubsection{Episodic Buffer}
\label{sec:EpisodicBuffer}
When considering the reading of text, it was found that participants were able to recall significantly more than 7$\pm$2 items of information. In 2000, a structure linking the STM and LTM was proposed by Baddely \cite{BaddeleyEpisodicBuffer}. The Episodic Buffer acts as a bridge between the LTM and STM, storing information too old to exist in the STM, without committing it to the LTM. This often occurs through the use of imagery to represent a set of concepts \cite{MemoryBaddeleyEysenkAnderson}. When applied to natural language, this memory structure allows the representation of a greater context than the STM alone.

\subsubsection{Disambiguation Models}
\label{sec:DisambiguationModels}
In some cases, when assigning meaning to words, ambiguity can arise. Some words have multiple concepts, for example, bank can refer to a building, or a sloped surface alongside a body of water. In such cases, the brain uses some process to select the correct concept. One such model of this disambiguation is the Multiple-Access model \cite{PsychologyOfLanguage}.

According to the Multiple-Access model, when presented with an ambiguious word, initially all corresponding concepts are activated \cite{AccessingLexicalAmbiguities}. The most appropriate concept is then chosen using a balance of context and frequency.

@@

%------------ WORDNET
\subsection{Wordnet}
\label{Wordnet}
In order to build a successful system, within the time bounds given by this project, a good, pre-existing, model of semantic memory is required. One such example of this is Wordnet \cite{WN1Introduction}.

@@

\label{Synsets}Central to the design of Wordnet, is the idea of synsets \cite{WN1Introduction}. The authors began using the assumption that all word meanings can be uniquely defined by their set of synonyms (words which share like meaning). In most cases, this assumption holds true, though, in cases where more detail is required, a "gloss", a brief defininition, was added \cite{WN1Introduction}.

@@

It is common knowledge that words can fall into one of a number of categories, nouns, adjectives, verbs and adverbs. G. Miller et al. note that, due to the differences in the relations between words in these categories, each type differs in the structure they imply, and are therefore held in different files \cite{WN1Introduction}. The proceeding subsections will go into each of these categories in more detail.

\subsubsection{Nouns}
\label{Nouns}
G. Miller et al. note that a noun can be defined using only its immediate hypernym, and how it differs from the other hyponyms of its immediate hypernym \cite{WN2Nouns}. From this, it can be seen that hyponymy is perhaps the most important relation in the organisation of nouns. For this reason, nouns form a strong hierachical structure in Wordnet.

Wordnet's designers stated the assumption that all nouns can be contained in a single hierachial structure \cite{WN2Nouns}. The issue with having a single word, of which all other words are hyponyms, is that this hypernym is relatively meaningless. It was instead decided to divide all words into 25 separate files, each containing a hierachical tree beginning with one of the following synsets \cite{WN2Nouns}:

@@

\subsubsection{Adjectives}
\label{Adjectives}
Adjectives are divisible into four distinct groups, each implying a different structure of semantic links \cite{WN3Adjectives}:
\begin{itemize}
	\item Descriptive Adjectives
	\begin{itemize}
		\item As stated in the \hyperref[Nouns]{previous section}, nouns have attributes. Descriptive adjectives act as modifiers for these attributes: for example, a building has a height, by saying "tall building", the height attribute is given a value \cite{WN3Adjectives}. Antonymy, defined \hyperref[Antonym]{previously}, is considered by wordnet's designers to be the most important relation between descriptive adjectives. Unfortuantely, not all adjectives have antonyms, leading to the designer's addition of an indirect antonym" semantic link, between synonyms of a word and its antonym \cite{WN3Adjectives}. These semantic links give rise to a structure made up of pairs, linked to one another by their synonyms.
	\end{itemize}

@@

	\item Colour Adjectives
	\begin{itemize}
		\item As their name suggests, colour adjectives concern the value of the colour attribute. This definition implies that these words should, in fact, fit into the descriptive adjective category. Their separation is given by colour adjectives lack of true antonym (excluding modifiers such as "light" and "dark") \cite{WN3Adjectives}. The lack of clear semantic relations between these words poses a problem for their organisation, leading wordnet's designers to link them using their definitions, i.e. using hue, lightness and saturation.
	\end{itemize}

@@

\textbf{Entailment} is a relation, simlar in nature to hyponymy. A verb (a) is said to entail another (b) if, when b is substituted for a in a sentence, the truth value of the sentence remains the same \cite{WN4Verbs}. For example, "run" entails "move", "she ran" can also be described by "she moved". If a entails b, and b entails a, a and b are synonyms.

@@

\subsubsection{Latent Semantic Analysis}
\label{sec:LSA}
In 1997, T. Laundaur and S. Dumais proposed a purely statistical method of semantic analysis, called Latent Semantic Analysis (LSA) \cite{LatentSemanticAnalysis}. The model can be visualised as a set of nodes, each representing a word, existing in semantic space. Words placed close together can be said to have similar meaning, and when close enough together, can be called synonyms.

@@

The authors found that, when presented with a synonym test, the model's best performance gave 64.4\% correct answers , which, when compared to US undergraduates for whom English is not their first language (scoring 64.5\% on average), could be considered to be reasonably effective \cite{LatentSemanticAnalysis}. This model only considers frequency, which, as discussed in the \hyperref[sec:DisambiguationModels]{Disambiguation Models section}, is only one of the two methods the brain is theorised to use for this process. By using a similar method in conjunction with a context focused model, a more accurate and useful model could be produced.

@@

As words in a document were encountered, all of its synsets were activated. All hypernyms, to a specified depth were also activated. The output of the system was the set of the most commonly seen synsets across the entire document, according to an equation similar to that discussed earlier in this subsection \cite{SeddingKazakov}.

@@

\subsubsection{Neural Networks}
\label{sec:NeuralNetwork}
In recent years the use of Neural Networks, more specifically deep learning Neural Networks, in the solving of computational problems has dramatically increased. More recently, this technique has been applied to the problem of natural language processing. From the description of Natural Language Processing given in the \hyperref[sec:IntroContext]{introduction}, we can see that a large proportion of NLP is the assigning of labels to tokens within a sentence. This process of labelling may also be interpreted as a categorisation problem, which Neural Networks are well suited to, and are often associated with \cite{NeuralNetworks}.

The first process requrired in the use of neural networks, is the conversion of raw text into a numeric, vector-based representation, capable of being processed. The sentence is then passed into the neural network \cite{NeuralNetworks}. The network proposed by R.Collobert and J. Weston in 2008 contained multiple layers, each serving its own purpose \cite{NeuralNetworks}. Initially the network identifies word features, before using this data to calculate the probability of each synset of each word.

@@

Unfortunately, the model failed to produce the correct synset significantly more accurately than the author's baseline (selecting the most common synset) \cite{MattBurkePrevious}. As suggested in the report, this may be due to semantic links, which occur in the brain, not being available or utilised by the model. Though, it may also be the case that the mathematical models used were inaccurate, with less linear functions being required.

The memory structures use may also have contributed to the result. Each item in the LTM had an activation \cite{MattBurkePrevious}. This activation is not present in the models developed by either Baddeley, or Shiffrin and Atkinson \cite{MemoryBaddeleyEysenkAnderson, ControlProcessesSTMAtkinson}.

@@

An implementation of the STM should have a finite size, falling in the range defined by G. Miller, 7$\pm$2.  Atkinson and Shiffrin’s model requires that the implemented STM contains items originating from a combination of the systems input, and LTM, each with an activation. The structure’s contents must also change, according to the arrival of new items, so as to correctly represent the local context of a section of text.

The system's LTM (Semantic Memory) requires knowledge of a large number of word meanings. Each of the meanings should be coupled with useful information consisting of a number of semantic links, connecting them to other meanings. As discussed in section \ref{Wordnet}, WordNet is a capable, pre-existing database, which follows a similar structure to the LTM defined by Baddeley. For this reason, it should be used to ensure that as much semantic information can be contained in the LTM as possible within the time scale of the project.

The addition of an Episodic Buffer may also be beneficial. Baddeley’s proposal may prove difficult to implement fully within the scope of this project, so design decisions must be made to simplify the model. With that said, its functionality must remain reasonably consistent, that is, the representation of wider context, for it to prove useful to the system.

@@

In the multiple access model, all relevant concepts are activated when a word is encountered.  A successful reading system should change the contents of the STM using a series of activations. If a concept already exists in the STM, Atkinson and Shiffrin’s model’s process of rehearsal should be employed, increasing the concept's activiation.

@@

Before a document can be inputted, it must have been syntactically analysed. Each word in a correctly preprocessed document will have a PoS tag, signifying its purpose in the sentence. This tag can then be used to minimise the size of the set of each word's possible definitions.

@@

Upon activation, the synset in question's activation is increased by an amount, dependant upon the hypernym model used (discussed later in this section). The same synset can be activated multiple times within the same sentence, an example of which is shown in Figure \ref{fig:HypernymAct}. In this case, a similar model to \hyperref[sec:MattBurke]{that proposed by M. Burke} \cite{MattBurkePrevious} is used: 
\[H = \sum\limits_{i=1}^N S_i\] 
The total activation increase of a synset is equal to the sum of all its activations within the sentence.

@@

\begin{itemize}
	\item The activation increase of the word's hypernyms must decrease as their generality increases, i.e.  as they become closer to the top of the tree.

@@

\subsubsection{Episodic Buffer}
\label{sec:ImplementedEpisodicBuffer}
The Episodic Buffer described in section \ref{sec:EpisodicBuffer} makes use of imagery to store information \cite{BaddeleyEpisodicBuffer}. A memory structure modelling this process exactly would not be possible within the scope of this project, therefore, a simplified model had to be created. In this simplified model, the Episodic Buffer still provides a memory for wider context, but does so using a synsets, not imagery.

@@

The most notable use of the Memory Controller is the activation of synsets. In order to activate a synset, the Memory Controller must take into account the whether the synset is present in any of the aforementioned memory structures, and handle the activation accordingly. The activateSynset function, shown in Listing \ref{lst:activateSynset} is responsible for handling this process.

@@

\subsubsection{Context}
\label{sec:DisambiguationContext}
The first approach attempted by the system makes use of the local context of a word. This context is held in the STM, and used in conjunction with knowledge of noun-verb relationships (the latter is discussed in Section \ref{sec:Sanity}). Two algorithms for disambiguation using this approach have been implemented, one using hyponyms and one using hypernyms.

@@

It may be noted that sanityCheck only considers verb incorrectness. As stated in the \hyperref[Verbs]{WordNet section}, for each word, there is likely to be a larger set of synsets when compared to nouns. With this knowledge, we can assume that the likelihood of an incorrect result for a verb is higher than that of a noun.

@@

For the purposes of parameter adjustment, the system will be tested on a single document. By limiting the input size, the time taken for each test can be reduced. Though appropriate for parameter tuning, it can be seen that a limited input size will not provide a good indication of general performance. For this reason, after parameter tuning has occured, the optimal values will be used in a more thorough evaluation test. This test will provide an input of 5 documents, ranging accross a variety of topics.

@@

The aim of the STM is to represent the local context of a word during the disambiguation phase. This requires of degree of generality in the contents of the STM, in order to  provide a wider view of a set of sentence's contents. A high number of synsets directly seen would imply that either, the local context of a word is not strong, or the contents of the STM are less general than intended. The latter can be seen as a failure to correctly represent the local context. An effective STM would contain hypernyms of the words in each sentence, meaning the more general concepts of the context are represented.

@@

When tested, this system performs significantly better than \hyperref[sec:EvFrequency]{random chance}, with an accuracy of 12\%. Even though it is an improvement, it can be seen that frequency alone does not produce a satisfying result. From this, we can tell that frequency only plays a small part in the disambiguation of text, and contextual information is required for a more effective system.

@@

Given the results of this test, it has been decided that 5 is the optimal size for the STM. When presented with a larger number of test documents, the system performs with an accuracy of 35\%, having 45\% of synsets directly seen in the STM. This is significantly better performance than \hyperref[sec:EvFrequency]{ a system based solely on frequency}.

@@

Given the results shown in table \ref{table:bActivation}, it can be seen that a value of 1 for $b$, achieves the best balance between accuracy and the number of synsets directly seen. With more testing data, the system produces an accuracy of 35\%. This is no improvement from the previously used method. Though the accuracy has remained consistent, only 39\% of synsets were directly seen, implying more generality in the STM, without loss of performance.

\subsection{Episodic Buffer}
\label{sec:EvEpisodicBuffer}
The episodic buffer, described in section \ref{sec:ImplementedEpisodicBuffer} aims to provide a more global context than the STM. With the functionality of the buffer being relatively simple, only one variable exists, the boost provided by a previously seen synset, with a greater boost giving global context a larger impact on disambiguation. The size of this boost will be varied between 0 (i.e. no episodic buffer) and 2.

@@

When observing the performance of the noun STM, it can be seen that there exists some abiguity, with some words having multiple possible meanings in the STM. In these cases, it can be seen that there exist few possible options for each word. From this we can say that the system has minimised the number of possibile meanings for each word.

When compared to the noun STM, the verb STM contains much more abiguity. This is likely due, in part, to the larger number of possible meanings for each word. This effect was not unexpected,hence the inclusion of sanity checks, described in section \ref{sec:Sanity} Though these were shown to be ineffective in section \ref{sec:EvDisSanity}.

@@

\section{Conclusions}
\label{sec:Conclusions}
This project has aimed to utilise previously established psychological models of disambiguation, and apply them to the problem of Semantic Analysis. The models used are those originally developed by Atkinson and Shiffrin \cite{ControlProcessesSTMAtkinson}, and then later further studied by Baddeley, to ultimately produce the Working Memory Model \cite{MemoryBaddeleyEysenkAnderson}.

@@

	\item \textbf{Reading System} \newline
		The system uses activation and forgetting to model the same processes which exist in Atkinson and Shiffrin's model \cite{ControlProcessesSTMAtkinson}. As the input corpus is read, these processes occur for each word, causing context to be represented by the STM and Episodic Buffer.
